\bf Excuse me, do you have a moment to talk about version control?

### 2017-07-06 README.Rmd
Rationalize citation / linking of RStudio, Git

Now the bad news: Git was built neither for the exact usage described here, nor for broad usability. You will undoubtedly notice this, so it's best to know in advance. Happily, there are many helpful tools that mediate your interactions with Git. GitHub itself is a fine example, as is [RStudio](https://www.rstudio.com/products/rstudio/). In addition to pointing out tools that soften Git's sharpest edges, I recommend specific habits and attitudes that reduce frustration.

@@

[Git](http://git-scm.com) is a __version control system__. Its original purpose 
was to help groups of developers work collaboratively on big software projects. 
Git manages the evolution of a set of files -- called a __repository__ or 
__repo__ -- in a sane, highly structured way. It is like the "Track 
Changes" feature from Microsoft Word, but more rigorous, powerful, and scaled up
to multiple files.

@@

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Figure \ref{fig:diy-vs-git}A). In collaborative settings based on email distribution, the original file swiftly becomes the root of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve Figure \ref{fig:diy-vs-git}B).

@@

We've introduced Git's powerful structure for file management, so where does GitHub fit in? [GitHub](https://github.com) complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

@@

* Install a local Git client, *optional but highly recommended*. A Git client 
provides a graphical user interface for Git, which is otherwise
command-line only. If you are an R user, you will find that 
[RStudio](https://www.rstudio.com/products/rstudio-desktop/) provides a great 
deal of this functionality. There are some notable gaps, however, so you might 
still choose to install a dedicated and comprehensive Git client such as 
[SourceTree](https://www.sourcetreeapp.com) or
[GitKraken](https://www.gitkraken.com). Git just operates on files, so you can
do some operations from RStudio, others from SourceTree, and others from the
shell.

@@

I targeted [GitHub](https://github.com) -- not [Bitbucket](https://bitbucket.org) or [GitLab](https://about.gitlab.com) -- for the sake of specificity. However, all the big-picture principles and even some mechanics will carry over to these alternative hosting platforms. I am advocating for the use of hosted version control as a general concept, with GitHub being the best and most common provider today. I note that many companies and even universities are starting to make GitHub Enterprise or GitLab available internally. For example, we host our own instance of GitHub Enterprise at UBC to support our Master of Data Science program

>>>>

Now the bad news: Git was built neither for the exact usage described here, nor
for broad usability. You will undoubtedly notice this, so it's best to know in
advance. Happily, there are many helpful tools that mediate your interactions
with Git. GitHub itself is a fine example, as is
[RStudio](https://www.rstudio.com/products/rstudio/) [@rstudio]. In addition to
pointing out tools that soften Git's sharpest edges, I recommend specific habits
and attitudes that reduce frustration.

@@

Git is a __version control system__. Its original purpose was to help groups of
developers work collaboratively on big software projects. Git manages the
evolution of a set of files -- called a __repository__ or __repo__ -- in a sane,
highly structured way. It is like the "Track Changes" feature from Microsoft
Word, but more rigorous, powerful, and scaled up to multiple files.

@@

Many people who don't use Git unwittingly re-invent a poor man's version of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of the iris data, captured in a single R source file. With informal version control, contributors create derivative copies of `iris.R`, decorating the file name with initials, dates, and other descriptors. Even when working alone, this leads to multiple versions of `iris.R` of indeterminate relatedness (Figure \ref{fig:diy-vs-git}A). In collaborative settings based on email distribution, the original file swiftly becomes part of a complicated phylogeny that no amount of "Track changes" and good intentions can resolve Figure \ref{fig:diy-vs-git}B).

@@

We've introduced Git's powerful structure for file management, so where does GitHub fit in? GitHub complements Git by providing a slick user interface and distribution mechanism for Git repositories. Git is the software you will use locally to record changes to a set of files. GitHub is a hosting service that provides a Git-aware home for such projects on the internet. These relationships are shown in Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive, but more structured, powerful, and programmatic.

@@

* Install a local Git client, *optional but highly recommended*. A Git client 
provides a graphical user interface for Git, which is otherwise command-line
only. If you are an R user, you will find that RStudio provides a great deal of
this functionality. There are some notable gaps, however, so you might still
choose to install a dedicated and comprehensive Git client such as 
[SourceTree](https://www.sourcetreeapp.com) or 
[GitKraken](https://www.gitkraken.com). Git just operates on files, so you can 
do some operations from RStudio, others from SourceTree, and others from the 
shell.

@@

I targeted GitHub -- not [Bitbucket](https://bitbucket.org) or
[GitLab](https://about.gitlab.com) -- for the sake of specificity. However, all
the big-picture principles and even some mechanics will carry over to these
alternative hosting platforms. I am advocating for the use of hosted version
control as a general concept, with GitHub being the best and most common
provider today. I note that many companies and even universities are starting to
make GitHub Enterprise or GitLab available internally. For example, we host our
own instance of GitHub Enterprise at UBC to support our Master of Data Science
program

### 2017-07-06 README.tex
Rationalize citation / linking of RStudio, Git

Now the bad news: Git was built neither for the exact usage described
here, nor for broad usability. You will undoubtedly notice this, so it's
best to know in advance. Happily, there are many helpful tools that
mediate your interactions with Git. GitHub itself is a fine example, as
is \href{https://www.rstudio.com/products/rstudio/}{RStudio}. In
addition to pointing out tools that soften Git's sharpest edges, I
recommend specific habits and attitudes that reduce frustration.

@@

\href{http://git-scm.com}{Git} is a \textbf{version control system}. Its
original purpose was to help groups of developers work collaboratively
on big software projects. Git manages the evolution of a set of files --
called a \textbf{repository} or \textbf{repo} -- in a sane, highly
structured way. It is like the ``Track Changes'' feature from Microsoft
Word, but more rigorous, powerful, and scaled up to multiple files.

@@

Many people who don't use Git unwittingly re-invent a poor man's version
of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of
the iris data, captured in a single R source file. With informal version
control, contributors create derivative copies of \texttt{iris.R},
decorating the file name with initials, dates, and other descriptors.
Even when working alone, this leads to multiple versions of
\texttt{iris.R} of indeterminate relatedness (Figure
\ref{fig:diy-vs-git}A). In collaborative settings based on email
distribution, the original file swiftly becomes the root of a
complicated phylogeny that no amount of ``Track changes'' and good
intentions can resolve Figure \ref{fig:diy-vs-git}B).

@@

We've introduced Git's powerful structure for file management, so where
does GitHub fit in? \href{https://github.com}{GitHub} complements Git by
providing a slick user interface and distribution mechanism for Git
repositories. Git is the software you will use locally to record changes
to a set of files. GitHub is a hosting service that provides a Git-aware
home for such projects on the internet. These relationships are shown in
Figure \ref{fig:yours-theirs-github}. GitHub is like DropBox or Google
Drive, but more structured, powerful, and programmatic.

@@

\begin{itemize}
\item
  Register for a free account with GitHub.
\item
  Install Git. Depending on your OS, Git might already be installed. But
  many will need to install it or will choose to update to a more recent
  version. Some basic configuration is critical, such as setting your
  username and email.
\item
  Install a local Git client, \emph{optional but highly recommended}. A
  Git client provides a graphical user interface for Git, which is
  otherwise command-line only. If you are an R user, you will find that
  \href{https://www.rstudio.com/products/rstudio-desktop/}{RStudio}
  provides a great deal of this functionality. There are some notable
  gaps, however, so you might still choose to install a dedicated and
  comprehensive Git client such as
  \href{https://www.sourcetreeapp.com}{SourceTree} or
  \href{https://www.gitkraken.com}{GitKraken}. Git just operates on
  files, so you can do some operations from RStudio, others from
  SourceTree, and others from the shell.
\item
  Confirm, with a practice repository, that local Git can send and
  receive the current version of the repository on GitHub, known as
  \textbf{pushing} and \textbf{pulling}, respectively.
\end{itemize}

@@

I targeted \href{https://github.com}{GitHub} -- not
\href{https://bitbucket.org}{Bitbucket} or
\href{https://about.gitlab.com}{GitLab} -- for the sake of specificity.
However, all the big-picture principles and even some mechanics will
carry over to these alternative hosting platforms. I am advocating for
the use of hosted version control as a general concept, with GitHub
being the best and most common provider today. I note that many
companies and even universities are starting to make GitHub Enterprise
or GitLab available internally. For example, we host our own instance of
GitHub Enterprise at UBC to support our Master of Data Science program

>>>>

Now the bad news: Git was built neither for the exact usage described
here, nor for broad usability. You will undoubtedly notice this, so it's
best to know in advance. Happily, there are many helpful tools that
mediate your interactions with Git. GitHub itself is a fine example, as
is \href{https://www.rstudio.com/products/rstudio/}{RStudio}
\citep{rstudio}. In addition to pointing out tools that soften Git's
sharpest edges, I recommend specific habits and attitudes that reduce
frustration.

@@

Git is a \textbf{version control system}. Its original purpose was to
help groups of developers work collaboratively on big software projects.
Git manages the evolution of a set of files -- called a
\textbf{repository} or \textbf{repo} -- in a sane, highly structured
way. It is like the ``Track Changes'' feature from Microsoft Word, but
more rigorous, powerful, and scaled up to multiple files.

@@

Many people who don't use Git unwittingly re-invent a poor man's version
of it. Figure \ref{fig:diy-vs-git} depicts a hypothetical analysis of
the iris data, captured in a single R source file. With informal version
control, contributors create derivative copies of \texttt{iris.R},
decorating the file name with initials, dates, and other descriptors.
Even when working alone, this leads to multiple versions of
\texttt{iris.R} of indeterminate relatedness (Figure
\ref{fig:diy-vs-git}A). In collaborative settings based on email
distribution, the original file swiftly becomes part of a complicated
phylogeny that no amount of ``Track changes'' and good intentions can
resolve Figure \ref{fig:diy-vs-git}B).

@@

We've introduced Git's powerful structure for file management, so where
does GitHub fit in? GitHub complements Git by providing a slick user
interface and distribution mechanism for Git repositories. Git is the
software you will use locally to record changes to a set of files.
GitHub is a hosting service that provides a Git-aware home for such
projects on the internet. These relationships are shown in Figure
\ref{fig:yours-theirs-github}. GitHub is like DropBox or Google Drive,
but more structured, powerful, and programmatic.

@@

\begin{itemize}
\item
  Register for a free account with GitHub.
\item
  Install Git. Depending on your OS, Git might already be installed. But
  many will need to install it or will choose to update to a more recent
  version. Some basic configuration is critical, such as setting your
  username and email.
\item
  Install a local Git client, \emph{optional but highly recommended}. A
  Git client provides a graphical user interface for Git, which is
  otherwise command-line only. If you are an R user, you will find that
  RStudio provides a great deal of this functionality. There are some
  notable gaps, however, so you might still choose to install a
  dedicated and comprehensive Git client such as
  \href{https://www.sourcetreeapp.com}{SourceTree} or
  \href{https://www.gitkraken.com}{GitKraken}. Git just operates on
  files, so you can do some operations from RStudio, others from
  SourceTree, and others from the shell.
\item
  Confirm, with a practice repository, that local Git can send and
  receive the current version of the repository on GitHub, known as
  \textbf{pushing} and \textbf{pulling}, respectively.
\end{itemize}

@@

I targeted GitHub -- not \href{https://bitbucket.org}{Bitbucket} or
\href{https://about.gitlab.com}{GitLab} -- for the sake of specificity.
However, all the big-picture principles and even some mechanics will
carry over to these alternative hosting platforms. I am advocating for
the use of hosted version control as a general concept, with GitHub
being the best and most common provider today. I note that many
companies and even universities are starting to make GitHub Enterprise
or GitLab available internally. For example, we host our own instance of
GitHub Enterprise at UBC to support our Master of Data Science program
